Title of Paper

### 2017-02-14 paper.tex
update validation

%======================================================================
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage[binary-units]{siunitx}
\usepackage{gensymb}
\sisetup{group-separator={,},
	detect-all,
	binary-units,
	list-units = single,
	range-units = single,
	range-phrase = --,
	per-mode = symbol-or-fraction,
	separate-uncertainty = true,
	multi-part-units = single,
	list-final-separator = {, and }
	%    scientific-notation = fixed
}
%======================================================================
% Add your bibliography file here, replace template.bib
\addbibresource{paper.bib}
%======================================================================
% Replace "Reaction Kinetics" in the line below by your paper topic
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

In addition, the temperature rate of change using the constant-pressure assumption\footnote{Note: this refers to evaluation within a reaction sub-step in the operator splitting scheme.} is evaluated as:
\begin{equation}
\frac{\text{d}[T]}{\text{d}t} = -\frac{\sum_{k}^{N_S} H^{\degree}_k \dot{\omega}_k}{\sum_{k}^{N_S} [C_k] c_{p_k}^{\degree}}
\end{equation}
although the code is equally capable of a evaluating the temperature rate using a constant-volume assumption, we omit this here for brevity.

@@

\subsection{Data Ordering and Vectorization Patterns}
For a chemical kinetic model with species $k$ for the $j$-th thermo-chemical state to be evaluated, $[C_k]_j$ there are two choices for data-storage in memory.
In the ``C'' (row-major) format, species concentrations for $j$-th thermo-chemical state are stored sequentially in memory, i.e.: $[C_0]_0\text{,}\allowbreak C[1]_0\ldots\allowbreak [C_{N_S}]_0\text{,}\allowbreak [C_0]_1\allowbreak\ldots\allowbreak [C_{N_S}]_N$, where $N$ is the total number of thermo-chemical conditions.
Alternatively, in the ``F'' (Fortan column-major) format species concentrations a single species for all thermo-chemical states are sequential, i.e.: $[C_0]_0\text{,}\allowbreak[C_0]\ldots\allowbreak[C_0]_N\text{,}\allowbreak[C_1]_0\ldots\allowbreak[C_{N_S}]_N$
In Sec.~\ref{results} the effect of this ordering will be shown to have a large performance impact on the program runtime.

@@

\section{Results and Discussion}

>>>>

%======================================================================
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage[binary-units]{siunitx}
\usepackage{gensymb}
\usepackage{amsmath}
\sisetup{group-separator={,},
	detect-all,
	binary-units,
	list-units = single,
	range-units = single,
	range-phrase = --,
	per-mode = symbol-or-fraction,
	separate-uncertainty = true,
	multi-part-units = single,
	list-final-separator = {, and }
	%    scientific-notation = fixed
}
%======================================================================
% Add your bibliography file here, replace template.bib
\addbibresource{paper.bib}
%======================================================================
% Replace "Reaction Kinetics" in the line below by your paper topic
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

In addition, the temperature rate of change using the constant-pressure assumption\footnote{Note: in this context, the ``constant-pressure assumption'' refers to evaluation within a reaction sub-step in the operator splitting scheme, rather than a general constant-pressure reactive-flow simulation.} is evaluated as:
\begin{equation}
\frac{\text{d}[T]}{\text{d}t} = -\frac{\sum_{k}^{N_S} H^{\degree}_k \dot{\omega}_k}{\sum_{k}^{N_S} [C_k] c_{p_k}^{\degree}}
\end{equation}
although the code is equally capable of a evaluating the temperature rate using a constant-volume assumption, we omit this here for brevity.

@@

\subsection{Data Ordering and Vectorization Patterns}
For a chemical kinetic model with species $k$ for the $j$-th thermo-chemical state to be evaluated, $[C_k]_j$ there are two choices for data-storage in memory.
In the ``C'' (row-major) format, species concentrations for $j$-th thermo-chemical state are stored sequentially in memory, i.e.: $[C_0]_0\text{,}\allowbreak C[1]_0\ldots\allowbreak [C_{N_S}]_0\text{,}\allowbreak [C_0]_1\allowbreak\ldots\allowbreak [C_{N_S}]_N$, where $N$ is the total number of thermo-chemical conditions.
Alternatively, in the ``F'' (Fortan column-major) format species concentrations a single species for all thermo-chemical states are sequential, i.e.: $[C_0]_0\text{,}\allowbreak[C_0]\ldots\allowbreak[C_0]_N\text{,}\allowbreak[C_1]_0\ldots\allowbreak[C_{N_S}]_N$
In Sec.~\ref{S:results} the effect of this ordering will be shown to have a large performance impact on the program runtime.

@@

\section{Results and Discussion}
\subsection{Validation}
The reaction rates of progress, species and temperature rates in this study are validated by comparison to Cantera~\cite{Cantera}, however due to the intricacies of floating point arithmetic care must be taken when comparing results.

In obtaining the net rate of progress of reaction $i$ from the forward and reverse rates of progress, $R_{i} = R_{i}^{\prime} - R_{i}^{\prime\prime}$, a base-10 bound on the loss of precision can be found as~\cite{goldberg1991every}:
\begin{equation}
2^{-p_i} \le \left\lvert 1 - \frac{R_{i}^{\prime}}{R_{i}^{\prime\prime}} \right\rvert \le 2^{-q_i}
\label{e:bounds}
\end{equation}
with $q_i \le p_i$, while $1 - \frac{R_{i}^{\prime}}{R_{i}^{\prime\prime}}$ can be computed with accurately via use of higher-precision numbers (in this case, via use of Python's Decimal class).

Plugging the forward and reverse rate constants from Cantera into Eq.~\eqref{e:bounds} we can obtain a reasonable a-priori precision bounds $\text{P}_{\text{min},i} = 2^{-p_i}$, $\text{P}_{\text{max},i} = 2^{-q_i}$.
Finally, when determining the error in the net rates of progress between this code and Cantera, the range of percent error attributable to precision loss, $\text{P}_{\text{err},i}$ can be found as:
\begin{equation}
\frac{\left\lvert\ R_{i,\text{CT}} - R_{i}\right\rvert}{\text{P}_{\text{min},i}} \le
\frac{\text{P}_{\text{err},i}}{100} \le \frac{\left\lvert R_{i,\text{CT}} - R_{i} \right\rvert}{\text{P}_{\text{max},i}}
\label{e:rel_bound}
\end{equation}
where the \text{CT} subscript indicates values from Cantera.
Note that the differences in Eq.~\eqref{e:rel_bound} are not subject to the same scrutiny as when computing the net rate of progress, namely because if they were small enough to merit this analysis the error would be minimal anyways.

With this we can properly validate the code against Cantera, as seen in Table~\todo[inline]{this}

\subsection{Results}
\label{S:results}
